---
title: "<br><br><br><br>Construction Workforce Development Strategy"
output: 
  slidy_presentation:
    css: style.css
---


```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(flextable)
library(officer)
knitr::opts_chunk$set(echo = FALSE)
saved_stuff <- readRDS(here("out","saved_stuff.rds"))
knitr::opts_template$set(fullwidth = list(
  fig.width = 16, fig.height = 7,
  fig.retina = 2, out.width = '100%'
))
```

## Construction information provided to Stokes:

```{r, opts.label='fullwidth'}
saved_stuff$to_stokes
```

## 2022 LMO labour market tightness:

```{r, opts.label='fullwidth'}
saved_stuff$res_heat
```

## 2022 LMO labour market tightness:

```{r, opts.label='fullwidth'}
saved_stuff$non_res_heat
```

## 2022 LMO labour market tightness:

```{r, opts.label='fullwidth'}
saved_stuff$heavy_heat
```

## 2022 LMO labour market tightness:

```{r, opts.label='fullwidth'}
saved_stuff$special_heat
```

## 2022 LMO for the 4 construction sub-industries.

```{r, opts.label='fullwidth'}
saved_stuff$lmo_plots
```

## Major Project Inventory: job loss due to completion

```{r, opts.label='fullwidth', warning=FALSE}
saved_stuff$mpi_plot
```

## MPI: historic conversion rates

* Roughly 40% of proposed projects pre 2012 started construction by 2022.

```{r, ft.left=1.75, ft.top=1.75}
saved_stuff$status_post_2011 %>%
  flextable() %>%
  theme_zebra()%>%
  autofit()
```

## Length of time spent in inventory prior to the start of construction

```{r, opts.label='fullwidth', warning=FALSE}
saved_stuff$waiting_time_MPI
```

## MPI: proposed construction start dates  

* Most pre-construction projects do not predict a construction start date.


```{r, ft.left=1.75, ft.top=1.75}
saved_stuff$unstarted%>%
  flextable() %>%
  theme_zebra()%>%
  autofit()
```



